Making Sequential Programs Deterministic

### 2019-04-05 java-design.tex
Edits in section 3.6

The return type of \codeid{System.getProperty} is usually \<@NonDet>. However,
the result is \<@Det> if the argument is \codeid{"line.separator"}; although
it varies by operating system, many programs including \<diff> and editors hide those
differences from the user.
The result is also deterministic for \codeid{"path.separator"} and
\codeid{"file.separator"}, because these lead to the same behavior given
corresponding environments.
The user can specify input properties that must be passed on the \<java>
command line and thus act like inputs to the program; these are also
treated as deterministic.

The inputs to a program are also treated as \<Det>.  That is, the type of
the formal parameter to \<main> is
\<@Det String @Det []>, a deterministic array of deterministic strings.

>>>>

The return type of \codeid{System.getProperty} is usually \<@NonDet>. However,
the result is \<@Det> if the argument is \codeid{"line.separator"}; although
it varies by operating system, many programs including \<diff> and editors hide those
differences from the user.
The result is also deterministic for \codeid{"path.separator"} and
\codeid{"file.separator"}, because these lead to the same behavior given
corresponding environments.
A user of \theDeterminismChecker can specify Java properties that must be passed on the \<java>
command line and thus act like inputs to the program;
\theDeterminismChecker treats these as deterministic.

The inputs to a program are also treated as deterministic.  That is, the type of
the formal parameter to \<main> is
\<@Det String @Det []>, a deterministic array of deterministic strings.
